First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He

### 2018-07-04 eg6-letters/incoherent/incoherent_prl.tex
Some edits on the incoherent paper

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurements in incoherent 
   deeply virtual Compton scattering (DVCS) off $^4$He using the exclusive 
   final state. The data were accumulated using a 6 GeV longitudinally 
   polarized electron beam incident on a pressurized $^4$He gaseous target 
   placed in front of the CLAS spectrometer in Hall-B at the Thomas Jefferson 
   National Accelerator Facility. The azimuthal angular ($\phi$) dependence of 
   the BSA is studied in a wide range of virtual photon and scattered proton 
   kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
   nucleon have been compared with the one on the free proton. In the whole 
   kinematical region of our measurements, the BSA on the bound nucleon is 
   smaller by about $20\%$ to $30\%$, indicating possible medium modification 
   on the nucleon's partonic structure.  This measurement opens a new 
   opportunity to explore the origin of the EMC effect within the framework of 
   the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon, which is at the origin of almost all the
universe's visible matter. While elastic lepton-nucleon measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the features of momentum sharing between the 
constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}.  
With nuclear targets, these measurements have revealed the fact that the 
distribution of quarks in a nucleus is not a simple convolution of 
their distributions within nucleons, an observation known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the topic, see  
\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provides access to a three-dimensional imaging of partons within the 
generalized parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. Combining these measurements has enabled the first extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of exclusive DVCS from the $^{4}$He nucleus are a critical 
step towards providing similar 3-D pictures of the quark structure of the 
nucleus as a whole, via the coherent channel 
\cite{Airapetian:2009cga,Hattawy:2017woc}, and provide a new approach for 
understanding modifications of the partonic structure of the bound nucleons via 
the incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for these purposes as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. However, it remains simple 
enough that exact calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. Experimentally, we measure the squared sum of the 
Bethe-Heitler (BH) and the DVCS amplitudes, with the former is the process 
where the real photon is emitted by the incident or the scattered electron 
rather than the nucleon. The beam-spin asymmetry arises from the interference 
of these two terms and is directly sensitive to the DVCS amplitude that contain 
the information on the GPDs.  Using a longitudinally polarized electron beam 
(L) and an unpolarized target (U), this beam-spin asymmetry observable is 
defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
beam-spin asymmetry can be simplified as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors and $x_B$ the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  
\begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
skewing factor and can be
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at an energy of 6.064 GeV. The data were accumulated over 
40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
target centered at 64~cm upstream of the CEBAF Large Acceptance Spectrometer 
(CLAS) coordinate center. For DVCS experiments, the CLAS baseline design 
\cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
solenoid magnet. The IC extends the photon detection acceptance of CLAS to very 
small polar angles, 4$^{\circ}$.  The 5-Tesla solenoid magnet in the center of 
which the target was located prevented the high-rate low-energy M{\o}ller 
electrons from reaching the CLAS drift chambers by guiding these electrons 
inside a tungsten shield placed around the beam line.

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state. Electrons were identified as negatively 
charged tracks reconstructed in the drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a light yield above the 
threshold in the Cherenkov counters. The protons were identified from 
positively charged tracks by timing analysis using the time-of-flight measured 
by the scintillator counters.  In addition, it was required that both the 
electron and the proton in the event originated from the same vertex at the 
target within CLAS tracking vertex resolution. The photons were detected in 
either the IC or the CLAS electromagnetic calorimeter. All the clusters within 
the IC fiducial region were assumed to be photons, while a timing cut is used 
to clean the EC photons from neutrons. Note that even though the DVCS reaction 
has only one real photon in the final state, events with more than one photon 
were not discarded at this stage. These are mostly soft photons from accidental 
coincidence which, as will be discussed below, the DVCS exclusivity cuts 
eliminate easily. In the following selection stage, the most energetic photon 
is considered as the DVCS photon candidate (see \cite{Hattawy:thesis} for 
additional details on the particles identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region.  
The $t$, transferred momentum squared to the recoil proton by assuming an 
on-shell proton at rest, was required to be greater than a minimum allowed 
value at given Q$^2$ and W ($t~>~t_{min}$).  Then, the exclusivity of the 
incoherent DVCS events was ensured by imposing constraints on the kinematical 
variables resulting from conserving the four-momentum in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables and applied cuts are shown in FIG.~\ref{fig:kin-cuts} (see 
\cite{Hattawy:thesis} for additional details). We also rejected events where a 
$\pi^0$ was identified by the invariant mass of two photons. About 30k events 
passed all these requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
events due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
with particles originated from different electron scattering events, their contribution 
was evaluated to be of 6.5\% by selecting events passing all our cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using the data and 
simulation. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection 
cuts to the number of identified $\pi^0$ events, 
$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of yield of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$ with the two photons detected. Depending on the 
kinematics, we found this contamination to be of 8\% to 10\%.

@@

In the kinematical phase-space of our experiment, the GPD $H$ dominants the 
contribution in the beam-spin asymmetry over the other three GPDs. Therefore, 
the $\phi$ dependence of $A_{LU}$ gives a direct access to the real and 
imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$, $a_1$, 
and $a_2$ of equation \ref{eq:alu-simp}. The studies of  the free proton 
$A_{LU}$ measurements, \cite{Girod:2007aa}, have shown that the the pure DVCS 
contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with 
zero.

@@

In this work we carried out the first step towards measuring the 
``generalized'' EMC effect in order to understand the potential sources of 
nuclear effects at the partonic level within the GPDs framework. We construct 
the ratio of $A_{LU}$ for bound protons to that on free proton target measured 
using similar electron-beam energy and experimental setup.  
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the dependence of the 
beam-spin asymmetry ratio at $\phi$~=~90$^{\circ}$ on the kinematical variables 
$Q^2$, $x_B$, and $t$. The free proton asymmetries were interpolated from the 
published results \cite{Girod:2007aa}.

@@

The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
to the free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated from 
the quark-meson coupling model \cite{Guzey:2008fe}. In particular, at lower $x_B$, 
where the off-shell model predicts an enhancement of the ratio, our experiment 
shows a sharp drop. This measurement shows that an important nuclear effect is
missing from the existing models in order to explain this strong quenching of
the beam-spin asymmetry.

%conclusion
In summary, we have presented the first exclusive beam-spin asymmetry measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level.  The bound-proton 
beam-spin asymmetries is largely suppressed compared to the free proton 
results measured in a similar phase-space. This surprising result opens a new avenue 
for progress in the understanding of the quarks and gluons behavior in the
nuclear medium.

@@

@@

\bibitem{Dupre:2017upj} R.~Dupr\'e {\it et al.},
  arXiv:1706.10160.

>>>>

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurements in incoherent 
   deeply virtual Compton scattering (DVCS) off $^4$He. The data were 
   accumulated using a 6 GeV longitudinally 
   polarized electron beam incident on a pressurized $^4$He gaseous target 
   placed in front of the CLAS spectrometer in Hall-B at the Thomas Jefferson 
   National Accelerator Facility. The azimuthal angular ($\phi$) dependence of 
   the BSA is studied in a wide range of virtual photon and scattered proton 
   kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
   nucleon have been compared with the one on the free proton. In the whole 
   kinematical region of our measurements, the BSA on the bound nucleon is 
   smaller by $20\%$ to $40\%$, indicating possible medium modification 
   on the nucleon's partonic structure. This measurement opens a new 
   opportunity to explore the origin of the EMC effect within the framework of 
   the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon. While elastic lepton-nucleon measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the features of momentum sharing between the 
constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}.  
With nuclear targets, these measurements have revealed the fact that the 
distribution of quarks in a nucleus is not a simple convolution of 
their distributions within nucleons, an observation known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the topic, see  
\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provides access to a three-dimensional imaging of partons within the 
generalized parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. Combining these measurements has enabled the first extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical 
step towards providing a similar 3-D pictures of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
the coherent channel where the nucleus is left intact \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a nucleon.
The latter, which is the focus of this letter, provides a unique access to the 
modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. Experimentally, we measure the squared sum of the 
Bethe-Heitler (BH) and the DVCS amplitudes, with the BH the process 
where the real photon is emitted by the incident or the scattered electron 
rather than the nucleon. The BSA arises from the interference 
of these two terms and is directly sensitive to the DVCS amplitude that contain 
the information on the GPDs.  Using a longitudinally polarized electron beam 
(L) and an unpolarized target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
BSA can be simplified as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors and $x_B$ the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  
\begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
skewing factor and can be
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at an energy of 6.064 GeV. The data were accumulated over 
40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
target centered at 64~cm upstream of the CEBAF Large Acceptance Spectrometer 
(CLAS) coordinate center. For DVCS experiments, the CLAS baseline design 
\cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
solenoid magnet. The IC extends the photon detection acceptance of CLAS down 
to a polar angle of 4$^{\circ}$. The 5-Tesla solenoid magnet in the center of 
which the target was located prevented the high-rate low-energy M{\o}ller 
electrons from reaching the CLAS drift chambers by guiding these electrons 
inside a tungsten shield placed around the beam line.

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state. Electrons were identified as negatively 
charged tracks reconstructed in the drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a light yield above the 
threshold in the Cherenkov counters. The protons were identified from 
positively charged tracks based on their time-of-flight measured 
by the scintillator counters.  In addition, it was required that both the 
electron and the proton in the event originated from the same vertex at the 
target within CLAS tracking vertex resolution. The photons were detected in 
either the IC or the CLAS electromagnetic calorimeter. All the clusters within 
the IC fiducial region were assumed to be photons, while a timing cut is used 
to clean the EC photons from neutrons. Note that even though the DVCS reaction 
has only one real photon in the final state, events with more than one photon 
were not discarded at this stage. These extra photons are mostly soft photons from accidental 
coincidence which, as will be discussed below, the DVCS exclusivity cuts 
eliminate easily. In the following selection stage, the most energetic photon 
is considered as the DVCS photon candidate (see \cite{Hattawy:thesis} for 
additional details on the particles identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region.  
The $t$, transferred momentum squared to the recoil proton by assuming an 
on-shell proton at rest, was required to be greater than a minimum allowed 
value at given Q$^2$ and W ($t~>~t_{min}$).  Then, the exclusivity of the 
incoherent DVCS events was ensured by imposing constraints on the kinematical 
variables resulting from conserving the four-momentum in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables and applied cuts are shown in FIG.~\ref{fig:kin-cuts} (see 
\cite{Hattawy:thesis} for additional details). We also rejected events where a 
$\pi^0$ was identified by the invariant mass of two photons. At the end of
this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
data. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correcltly identified as exclusive $ep\rightarrow e'p'\pi^0$, 
$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$. Depending on the 
kinematics, we found this contamination to be of 8 to 10\%.

@@

In the kinematical phase-space of our experiment, the GPD $H$ dominates the 
contribution in the BSA over the other three GPDs. Therefore, 
the $\phi$ dependence of $A_{LU}$ gives a direct access to the real and 
imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$, $a_1$, 
and $a_2$ of equation \ref{eq:alu-simp}. The studies of  the free proton 
$A_{LU}$ measurements, \cite{Girod:2007aa}, have shown that the the pure DVCS 
contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with 
zero.

@@

In this work we carried out the first step towards measuring the 
``generalized'' EMC effect in order to understand the potential sources of 
nuclear effects at the partonic level within the GPDs framework. We construct 
the ratio of $A_{LU}$ for bound protons to that on free proton target measured 
using similar electron-beam energy and experimental setup.  
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the dependence of the 
BSA ratio at $\phi$~=~90$^{\circ}$ on the kinematical variables 
$Q^2$, $x_B$, and $t$. The free proton asymmetries were interpolated from the 
published results \cite{Girod:2007aa}.

@@

The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
to the free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated from 
the quark-meson coupling model \cite{Guzey:2008fe}. In particular, at lower $x_B$, 
where the off-shell model predicts an enhancement of the ratio, our experiment 
shows a sharp drop. This measurement shows that an important nuclear effect is
missing from the existing models in order to explain this strong quenching of
the BSA.

%conclusion
In summary, we have presented our BSA measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level.  The bound-proton 
BSA is largely suppressed compared to the free proton 
results measured in a similar phase-space. This surprising result opens a new avenue 
for progress in the understanding of the quarks and gluons behavior in the
nuclear medium.

@@

\bibitem{Dupre:2015jha} 
  R.~Dupré and S.~Scopetta,
  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)

@@

\bibitem{Dupre:2017upj} 
  R.~Dupr\'e {\it et al.},
  Nucl.\ Instrum.\ Meth.\ A {\bf 898}, 90 (2018)
